Why do we Eval?\\[2mm]\Large A large-scale study of Eval usage in R

### 2020-11-28 inst/paper/main.tex
intro: removing core

\vspace{2mm}\noindent\emph{The What and How.} One significant benefit
of choosing R is that every package in the CRAN repository is curated
and comes with examples of typical usage. This gives us a large code
base that we can analyze dynamically. To observe \eval we built a
two-level monitoring infrastructure:\footnote{Our infrastructure is
open source and publicly available, our anonymized code is at {\tt
  http://url.com}, a more complete artifact will be submitted to the
artifact evaluation committee. } we can monitor R programs by
instrumentation --- this gives us access to many user-visible
properties of R programs --- but we can also monitor the inner working
of the R interpreter --- this allows us to capture details of
execution that are not exposed at the source level. Dynamic analysis
is of course limited in that it can only observe behaviors that are
triggered by the particular inputs passed to the program. Luckily,
CRAN libraries come with multiple input datasets and use-cases.

The choice of corpus is crucial for analyses like ours.  Our corpus
has been constructed to reflect the levels of sophistication of the R
community.  We distinguish between \emph{core packages} (there are
\CorpusCorePackages such packages that are distributed together with
the R virtual machine), \emph{CRAN packages} (\CorpusPackages curated
packages that pass stringent quality checks and are equipped with
tests and sample data), \emph{Kaggle scripts} (\CorpusFinishedKaggle
end-user written programs that performs a particular data analysis
task). It is reasonable to expect that \eval usage differ between
these datasets. The core R code is extremely stable, maintained for
the last 20 years with very few far reaching changes. The libraries
represent a more lively ecosystem with new libraries added each day.
Finally, end user code is often one-use scripts thrown together and
sometimes never revisited.

@@

\subsection{Infrastructure}

>>>>

\vspace{2mm}\noindent\emph{The What and How.} One significant benefit
of choosing R is that every package in the CRAN repository is curated
and comes with examples of typical usage. This gives us a large code
base that we can analyze dynamically. To observe \eval we built a
two-level monitoring infrastructure:\footnote{Our infrastructure is
open source and publicly available, our anonymized code is at {\tt
  http://url.com}, a more complete artifact will be submitted to the
artifact evaluation committee. } we can monitor R programs by
instrumentation --- this gives us access to many user-visible
properties of R programs --- but we can also monitor the
inner-workings of the R interpreter --- this allows us to capture
details not exposed at the source level. Dynamic analysis is limited,
it can only observe behaviors triggered by the particular inputs
passed to a program. Luckily, CRAN libraries come with many tests and
use-cases. The choice of corpus is crucial. Our corpus has been
constructed to reflect the levels of sophistication of the R
community. We distinguish between \emph{CRAN packages}
(\CorpusPackages curated packages that pass stringent quality checks
and are equipped with tests and sample data) and \emph{Kaggle scripts}
(\CorpusFinishedKaggle end-user written programs that performs a
particular data analysis task). It is reasonable to expect that \eval
usage differ between these datasets: the libraries represent a lively
ecosystem with new libraries added each day, while end user code is
often thrown together, run once, and never revisited.

@@

\subsection{Analysis Pipeline}
